---
title: "Food security causality"
author: "Louise Glew and David Gill"
date: "December 5, 2017"
output: html_document
---
Load necessary packages
```{r eval=FALSE}
library(plyr)
library(ggplot2)
library(reshape2)
library(varhandle)
library(xlsx)
library(RODBC)
library(Matching)
library(optmatch)
library(tidyr)
library(RItools)
library(Hmisc)
library(MBESS)
library(rbounds)
library(Kendall)
library(dplyr)
library(lavaan)
library(semPlot)
```
Source relevant scripts
```{r eval=FALSE}
# 1.2 Source relevant R code 
script.dir <- 'C:/Users/LocalAdmin/Documents/OneDrive - Conservation International 1/Data analysis/BHS/'
source('2_Social/SourcedScripts/BHS_MPA_Mystery.R')
source('2_Social/SourcedScripts/Function_variable_outcome.R') # function to calculate outcomes
source('2_Social/SourcedScripts/Matching_2yr_impacts_DG.R') # get match pairs (and retain match pairs)
#source(paste0(script.dir,'Matching 2yr_DG.R')) # get match pairs
source(paste0(script.dir,'Food security original variables_DG.R')) # get food security table w original indicators
source('2_Social/SourcedScripts/Function_summarise_bigfive_impacts.R') # get other ATTs
```

```{r eval=FALSE}
# -----
# 1.2 Import raw.data
# 2 year impact data
#HH.data <- read.delim("C:/Users/LocalAdmin/Dropbox/BHS/HHdata_raw_2015_0704.txt")

# -----
# 2.1 Compute fish consumption indicator
fish.consume<-HHData %>% 
  select(HouseholdID,FreqEatFishClean) %>%
### Convert all blind codes to missing values. Note '994' in this context represents non-fishers.
  mutate(FreqEatFishClean = ifelse(FreqEatFishClean>=995 | FreqEatFishClean==993 |is.na(FreqEatFishClean),
                              990,FreqEatFishClean),
         FreqEatFishClean=as.factor(FreqEatFishClean)) %>%
  rename(fish.consume=FreqEatFishClean)
summary(fish.consume$fish.consume)

# -----
# 2.2 Compute fish sale indicator
fish.sale.outcome<-HHData %>% 
  select(HouseholdID,FreqSaleFishClean) %>%
  ### Convert all blind codes to missing values. Note '994' in this context represents non-fishers.
  mutate(FreqSaleFishClean = ifelse(FreqSaleFishClean>=995 |FreqSaleFishClean==993 |is.na(FreqSaleFishClean),
                              990,FreqSaleFishClean)) %>%
  rename(fish.freq.sale=FreqSaleFishClean)
summary(fish.sale.outcome$fish.freq.sale)

# Pre-process data
fish.sale.MPA.t2 <- MPA.time.pairs %>%
  select(HouseholdID) %>%
  left_join(fish.sale.outcome,by=c("HouseholdID"))

# Time outcome (trend over time in MPA)
fish.sale.time <-Variable_outcome(MPA.time.pairs,fish.sale.outcome)

# Treatment outcome (across treatment and control)
fish.sale.tr <-Variable_outcome(MPA.rpt.xsection.pairs,fish.sale.outcome)

# Interaction outcome 
fish.sale.int <-Variable_outcome(MPA.int.xsection.pairs,fish.sale.outcome)

# Join three outcome sets and MPA at t2
fish.sale.ATT <- fish.sale.time %>%
  left_join(fish.sale.tr, by="HouseholdID") %>%
  left_join(fish.sale.int, by="HouseholdID") %>%
  left_join(fish.sale.MPA.t2, by="HouseholdID") %>%
  stats::setNames (c("HouseholdID","sale.mpa.t0","sale.c.t2","sale.c.t0", "sale.mpa.t2")) %>%
# Compute outcomes
  mutate(MPA.outcome=sale.mpa.t2 -sale.mpa.t0,
         control.outcome=sale.c.t2 -sale.c.t0,
         ATT=MPA.outcome-control.outcome)

```

## SEM models
Original model
```{r eval=F}
sem.data <-read.csv("C:/Users/LocalAdmin/Documents/OneDrive - Conservation International 1/Data analysis/BHS/sem_data.csv", sep=",")
head(sem.data)

# Original model
colnames(sem.data)<-c("HouseholdID","Y","MPAID","X","M1","M2","local.fish")
sem.data.reduced <-na.omit(sem.data)
model.org <-' # direct effect
          Y ~ a*X
          # mediator
          M1 ~ b*X
          M2 ~d*X
          Y ~ c*M1
          Y ~e*M2
          #indirect effects
          bcde := b*c*d*e
          #total effect
          total := a+(b*c*d*e)'
# Y: food security
# a: MPA to food security
# b: MPA to biomass (M1)
# d: MPA to tenure.control (M2)
# c: biomass to food security
# e: tenure to food security
fit.org<-sem(model.org,data=sem.data, std.lv=TRUE)
summary(fit.org)
```

Orginal model, rescaling biomass to similar scale to rest of variables
```{r eval=F}
colnames(sem.data)<-c("HouseholdID","food.sec","MPAID","MPA","tenure","biomass","local.fish")
#rescale biomass
sem.data$biomass1 <- sem.data$biomass/10
head(sem.data)
model.rescale <-' # direct effect
          food.sec ~ a*MPA
          # mediator
          biomass1 ~ b*MPA
          tenure ~d*MPA
          food.sec ~ c*biomass1
          food.sec ~e*tenure
          #indirect effects
          bcde := b*c*d*e
          #total effect
          total := a+(b*c*d*e)'
fit.rescale <-sem(model.rescale,data=sem.data, std.lv=TRUE)
summary(fit.rescale)
```
Failed: Model where food security is a latent variable, rescaling biomass to similar scale to rest of variables
```{r eval=F}
sem.data1 <- sem.data %>%
  left_join(select(hfoodsec,HouseholdID:FSHungry),by='HouseholdID') 
#  mutate(FSBalancedDiet1=1-FSBalancedDiet) %>%
#  select(-FSBalancedDiet)
#  na.omit()

cov(select(sem.data1,FSDidNotLast:FSHungry))
model.latentFS <-' 
# measurement model-food security definition
    food.sec1 =~ FSDidNotLast + FSBalancedDiet + FSAdultSkip + FSEatLess + FSFreqAdultSkip + FSHungry
          # direct effect
          food.sec1 ~ a*MPA
          # mediator
          biomass1 ~ b*MPA
          tenure ~d*MPA
          food.sec1 ~ c*biomass1
          food.sec1 ~e*tenure
          #indirect effects
          bcde := b*c*d*e
          #total effect
          total := a+(b*c*d*e)'
fit.latentFS <-sem(model.latentFS,data=sem.data1, std.lv=TRUE)
summary(fit.latentFS)
semPaths(fit1, "std",edge.label.cex=1.5, curvePivot=T, layout ="spring")
```

ATT model: Model where food security is a latent variable, rescaling biomass to similar scale to rest of variables
```{r eval=F}
add.food.data <-read.csv("C:/Users/LocalAdmin/Documents/OneDrive - Conservation International 1/Data analysis/BHS/additional_foodsec_data.csv", sep=",")
sem.data2 <- sem.data %>%
  left_join(add.food.data,by='HouseholdID')%>%
  left_join(select(fish.sale.ATT,HouseholdID,ATT),by='HouseholdID') %>%
  rename(fish.sale.ATT=ATT) %>%
  mutate(fish.sale.ATT=fish.sale.ATT/10) %>%
  left_join(select(tenure.ATT,HouseholdID,ATT),by='HouseholdID') %>%
  rename(tenure.ATT=ATT)
names(sem.data2)
model.ATT <-' 
# measurement model-food security definition
    food.sec1 =~ FSDidNotLast.ATT + FSBalancedDiet.ATT + FSAdultSkip.ATT + FSEatLess.ATT + FSFreqAdultSkip.ATT + FSHungry.ATT
          # direct effects
          food.sec1 ~ a*tenure.ATT
          food.sec1 ~ b*fish.sale.ATT
        # mediator
          fish.sale.ATT ~ c*biomass1
          #total effect
          total := (b*c)+a
#correlations
FSDidNotLast.ATT ~~ FSBalancedDiet.ATT
FSDidNotLast.ATT ~~ FSAdultSkip.ATT
FSDidNotLast.ATT ~~ FSEatLess.ATT
FSDidNotLast.ATT ~~ FSFreqAdultSkip.ATT
FSDidNotLast.ATT ~~ FSHungry.ATT 
FSBalancedDiet.ATT ~~ FSAdultSkip.ATT
FSBalancedDiet.ATT ~~ FSEatLess.ATT
FSBalancedDiet.ATT ~~ FSFreqAdultSkip.ATT
FSBalancedDiet.ATT ~~ FSHungry.ATT
FSAdultSkip.ATT ~~ FSEatLess.ATT
FSAdultSkip.ATT ~~ FSFreqAdultSkip.ATT
FSAdultSkip.ATT ~~ FSHungry.ATT
FSEatLess.ATT ~~ FSFreqAdultSkip.ATT
FSEatLess.ATT ~~ FSHungry.ATT
FSFreqAdultSkip.ATT ~~ FSHungry.ATT'
fit.ATT <-sem(model.ATT,data=sem.data2, std.lv=TRUE)
varTable(fit.ATT)
summary(fit.ATT)
semPaths(fit.ATT, "std",edge.label.cex=1.5, curvePivot=T, layout ="spring")

```

Other models
```{r eval=F}
model <- '# direct effect
          Y ~ a*X

          # mediators
          M1 ~ d*X
          M2 ~ c*X
          M3 ~ b*X
          M5 ~(e*M1)+(f*M2)
          M6 ~(g*M2)+(h*M3)
          Y ~ (j*M5)+(i*M6)
          
          # indirect effect      
          indirect := b*c*d*e*f*g*h*i*j

          #total effect
          total :=c +(b*c*d*e*f*g*h*i*j)
'
fit <-sem(model, data=sem.data, fit.measures=TRUE)
summary(fit)
```