---
title: "BHS dimension reduction"
author: "David Gill & Louise Glew"
date: "February 13, 2018"
output: html_document
---
Create custom functions, set stringsasFactors as false
```{r eval=F}

# load packages
pacman::p_load(plyr,ggplot2,reshape2,reldist,grid,gridExtra,varhandle,Rmisc,FD,
               RODBC,Matching,optmatch,tidyr,RItools,Hmisc,MBESS,rbounds,Kendall,corrplot,cowplot,dplyr)

# Options
options(scipen=999,stringsAsFactors = FALSE)

# Functions
sum2=function(x){sum(x,na.rm=TRUE)}
mean2=function(x){mean(x,na.rm=TRUE)}
Mode <- function(x) {
 ux <- unique(x)
 ux[which.max(tabulate(match(x, ux)))]
}

# Directories
outputdir <- "C:/Users/dgill6/Documents/Data analysis/BHS/"

# ggplot variables
pd <- position_dodge(width=.3) # move them .05 to the left and right
myColors <- matrix(c('deepskyblue3','darkblue'),nrow=1)

# Gender of household head
HHgender<-read.csv(file = "C:/Users/dgill6/Dropbox/BHS/clean_gender_HHH.csv", header = TRUE) 

```

### Compute variables for dimension reduction
Create 3 variables to compute social stratification scores (2 dimensions) from multiple variables in multi-dimensional space.

 1. fishing dependence (1:low, 3: high)
 2. gender of household head (1: male, 2: female)
 3. poverty quinitles/reverse material assets index 

```{r eval=F}
#grep("HH",names(data),value = T,ignore.case = T)
# Compute wealth quntiles
data <- HHData %>% 
 left_join(dplyr::select(BigFive,HouseholdID,MAIndex:SERate),by='HouseholdID')  %>% 
 left_join(MPANames,by='MPAID')  %>% 
 left_join(HHgender,by='HouseholdID') %>% 
  filter(!is.na(PrimaryLivelihoodClean)) %>% 
  filter(MonitoringYear=='Baseline') %>% 
 mutate(revMAIndex=-MAIndex,
        pov.quintile=as.numeric(cut2(-MAIndex, g=5)),
        fish.dep=ifelse(PrimaryLivelihoodClean==3,3,
                        ifelse(SecondaryLivelihoodClean==3 | TertiaryLivelihoodClean==3,2,1))) %>% 
  select(HouseholdID,MPAName,MAIndex,FSIndex,revMAIndex,fish.dep,IndividualGender,pov.quintile) %>% 
  filter(complete.cases(.))
plot(data$revMAIndex~data$pov.quintile) # should be negatively correlated
```
### create nMDS plots and export scores
We need to decide if we want to include more variables. Given that there are only 3 variables with few levels, there isn't much variation between individuals. I used a reverse of the MAIndex but some ugly plots came out!
```{r eval=F}
###- using poverty quintiles

# calculate gower distance (better for ordinal data) 
data_gow <- gowdis(select(data,fish.dep,IndividualGender,pov.quintile), ord = "podani")
#nMDS # 2 dimensions
nmds<-metaMDS(data_gow,center=T, trymax = 20, autotransform =F, k=2,pc=TRUE)
stressplot(nmds,main="Stress plot")
plot(nmds,main="Non-metric MDS (Gower Distance)")
ord.mds1 <- envfit(nmds ~ MAIndex, data=data, perm=999,na.rm = TRUE)
plot(ord.mds1)
abline(v=0);abline(h=0)
# rotate the graph so that one axis is correlated to the wealth index
nmds.varimax <- MDSrotate(nmds,data$MAIndex,na.rm=T) #rotate to have DA be its own axis
plot(nmds.varimax$points,main="Rotated nMDS")
ord.mds2 <- envfit(nmds.varimax$points ~ MAIndex, data=data, perm=999,na.rm = TRUE) 
plot(ord.mds2)
abline(v=0);abline(h=0)

###- using reverse MAIndex
# dissimilarity matrix: 
# data_gow <- gowdis(select(data,fish.dep,IndividualGender,revMAIndex), ord = "podani")
# #nMDS # 2 dimensions
# nmds<-metaMDS(data_gow,center=T, trymax = 20, autotransform =F, k=2,pc=TRUE)
# stressplot(nmds,main="Stress plot")
# plot(nmds,main="Non-metric MDS (Gower Distance)")
# ord.mds1 <- envfit(nmds ~ MAIndex, data=data, perm=999,na.rm = TRUE)
# plot(ord.mds1)
# abline(v=0);abline(h=0)
# # rotate the graph so that one axis is correlated to the wealth index
# nmds.varimax <- MDSrotate(nmds,data$MAIndex,na.rm=T) #rotate to have DA be its own axis
# plot(nmds.varimax$points,main="Rotated nMDS")
# ord.mds2 <- envfit(nmds.varimax$points ~ MAIndex, data=data, perm=999,na.rm = TRUE) 
# plot(ord.mds2)
# abline(v=0);abline(h=0)

# export scores
data$nmds1 <- scores(nmds.varimax)[,1]
data$nmds2 <- scores(nmds.varimax)[,2]
head(data)

write.csv(select(data,HouseholdID,nmds1,nmds2),
          "C:/Users/dgill6/Dropbox/BHS/DG_nmds_scores.csv",row.names=F)


plot()
write.csv()
```