---
title: "data_checking_household"
output: html_notebook
---

```{r}

pacman::p_load(rio, plyr, foreach, dplyr, openxlsx, chron, tidyverse, reshape, xlsx)
```

```{r}
#load the household data
household_tbl <-
  import('INSERT FILE PATH HERE') %>%
  filter(!is.na(householdid))
#rename the column with typo in UNIPA dataset
names(household_tbl)[names(household_tbl) == "assetsattellite"] <- "assetsatellite"
#set column names in UNIPA to lower case
colnames(household_tbl) <- tolower(colnames(household_tbl))
#create skip codes list
skipcodes <- c(990:999)
```

Data frame summarizing number of NAs in each column: 
```{r}
count_NA_hh <- sapply(household_tbl, function(x) sum(is.na(x)))
count_NA_hh <- as.data.frame(count_NA_hh)
```

* RELIGION_CHOICES (variable name: `religion`)

```{r}
# Top section creating vectors of "legal" ranges for codes
religion_codes <- c(1:7)
# Bottom section that stores rows with invalid data
religion_index <- filter(household_tbl, !religion%in%c(religion_codes,skipcodes)) %>% select(householdid, religion)
# Option option 1
print(paste0("Values out of range for religion for Household ID", religion_index$householdid))
# Option option 2
print(religion_index)
```

* LATITUDE_DEGREE_CHOICES (`latdeg`)

```{r}
latdeg_codes <- c(0:90)
latdeg_index <- filter(household_tbl, !latdeg%in%c(latdeg_codes, skipcodes)) %>% select(householdid, latdeg)
print(paste0("Values out of range for latitude degree for Household ID", latdeg_index$householdid))
print(latdeg_index)
```

* LONGITUDE_DEGREE_CHOICES (`londeg`)

```{r}
londeg_codes <- c(0:180)
londeg_index <- filter(household_tbl, !londeg%in%c(londeg_codes,skipcodes)) %>% select(householdid, londeg)
print(paste0("Values out of range for longitude degree for Household ID", londeg_index$householdid))
print(londeg_index)
```

* MINUTES_SECONDS_CHOICES (`latmin`, `latsec`, `lonmin`, `lonsec`)

```{r}
min_sec_codes <- c(0:60)

# latitude minute index
latmin_index <- filter(household_tbl, !latmin%in%c(min_sec_codes,skipcodes)) %>% select(householdid, latmin)
print(paste0("Values out of range for latitude minute for Household ID", latmin_index$householdid))
print(latmin_index)

# latitude second index
latsec_index <- filter(household_tbl, !latsec%in%c(min_sec_codes,skipcodes)) %>% select(householdid, latsec)
print(paste0("Values out of range for latitude second for Household ID", latsec_index$householdid))
print(latsec_index)

# longitude minute index
lonmin_index <- filter(household_tbl, !lonmin%in%c(min_sec_codes,skipcodes)) %>% select(householdid, lonmin)
print(paste0("Values out of range for longitude minute for Household ID", lonmin_index$householdid))
print(lonmin_index)

# longitude second index
lonsec_index <- filter(household_tbl, !lonsec%in%c(min_sec_codes,skipcodes)) %>% select(householdid, lonsec)
print(paste0("Values out of range for longitue second for Household ID", lonsec_index$householdid))
print(lonsec_index)
```

* SECONDS_FRACTION_CHOICES (`latfrac`, `lonfrac`)

```{r}
sec_frac_codes <- c(0:9)

latfrac_index <- filter(household_tbl, !latfrac%in%c(sec_frac_codes,skipcodes)) %>% select(householdid, latfrac)
print(paste0("Values out of range for latitude fraction for Household ID", latfrac_index$householdid))
print(latfrac_index)

lonfrac_index <- filter(household_tbl, !lonfrac%in%c(sec_frac_codes,skipcodes)) %>% select(householdid, lonfrac)
print(paste0("Values out of range for longitude fraction for Household ID", lonfrac_index$householdid))
print(lonfrac_index)
```

* LATITUDE_SPHERE_CHOICES (`latsphere`)

```{r}
lat_sphere_codes <- c("N|n|North|north|S|s|South|south|990|991|992|993|995|996|997|998|999")
lat_sphere_index <- 
  filter(household_tbl, !grepl(lat_sphere_codes, latsphere)) %>%
  select(householdid, latsphere)

print(paste0("Values in incorrect format for latitude sphere for Household ID", lat_sphere_index$householdid))
print(lat_sphere_index)
```

* LONGITUDE_SPHERE_CHOICES (`lonsphere`)

```{r}
lon_sphere_codes <- c("E|e|East|east|W|w|West|west|990|991|992|993|995|996|997|998|999")
lon_sphere_index <- 
  filter(household_tbl, !grepl(lon_sphere_codes,lonsphere)) %>% 
  select(householdid, lonsphere)
print(paste0("Values in incorrect format for longitude sphere for Household ID", lon_sphere_index$householdid))
print(lon_sphere_index)
```

* DAY_OF_MONTH_CHOICES (`interviewday`)

```{r}
day_codes <- c(1:31)
day_index <- filter(household_tbl, !interviewday%in%c(day_codes, skipcodes)) %>% select(householdid, interviewday)
print(paste0("Values out of range for interview day for Household ID", day_index$householdid))
print(day_index)
```

* MONTH_CHOICES (`interviewmonth`)

```{r}
month_codes <- c(1:12)
month_index <- filter(household_tbl, !interviewmonth%in%c(month_codes, skipcodes)) %>% select(householdid, interviewmonth)
print(paste0("Values out of range for interview day month for Household ID", month_index$householdid))
print(month_index)
```

* YEAR_CHOICES (`interviewyear`)

```{r}
year_codes <- c(2000:2050)
year_index <- filter(household_tbl, !interviewyear%in%c(year_codes)) %>% select(householdid, interviewyear)
print(paste0("Values out of range for interview year for Household ID", year_index$householdid))
print(year_index)
```

* ECONOMIC_STATUS_TREND_CHOICES (`economicstatustrend`)

```{r}
econ_trend_codes <- c(1:5)
econ_trend_index <- 
  filter(household_tbl, !economicstatustrend%in%c(econ_trend_codes, skipcodes)) %>%
           select(householdid, economicstatustrend)
print(paste0("Values out of range for economic status strend for Household ID", econ_trend_index$householdid))
print(econ_trend_index)
```

* COOKING_FUEL_CHOICES (`cookingfuel`)

```{r}
cooking_fuel_codes <- c(1:5)
cooking_fuel_index <- 
  filter(household_tbl, !cookingfuel%in%c(cooking_fuel_codes, skipcodes)) %>%
           select(householdid, cookingfuel)
print(paste0("Values out of range for cooking fuel for Household ID", cooking_fuel_index$householdid))
print(cooking_fuel_index)
```

* YES_NO_CHOICES (`householddeath`, `householdbirth`, `fsadultskip`, `fseatless`, `fshungry`, `fschildportion`, `fschildskip`, `rightsaccess`, `rightsharvest`, `rightsmanage`, `rightsexclude`, `rightstransfer`, `marinegroup`, `othergroup`, `votedistrict`, `votenational`)

```{r}
yes_no_codes <- c(0:1)
yes_no_var_index_hh <- 
  filter(household_tbl, !householddeath%in%c(yes_no_codes, skipcodes)) %>%
           select(householdid, householddeath)
  filter(household_tbl, !householdbirth%in%c(yes_no_codes, skipcodes)) %>%
           select(householdid, householdbirth)
  filter(household_tbl, !fsadultskip%in%c(yes_no_codes, skipcodes)) %>%
           select(householdid, fsadultskip) 
  filter(household_tbl, !fseatless%in%c(yes_no_codes, skipcodes)) %>%
           select(householdid, fseatless) 
  filter(household_tbl, !fshungry%in%c(yes_no_codes, skipcodes)) %>%
           select(householdid, fshungry) 
  filter(household_tbl, !fschildportion%in%c(yes_no_codes, skipcodes)) %>%
           select(householdid, fschildportion) 
  filter(household_tbl, !fschildskip%in%c(yes_no_codes, skipcodes)) %>%
           select(householdid, fschildskip) 
  filter(household_tbl, !rightsaccess%in%c(yes_no_codes, skipcodes)) %>%
           select(householdid, rightsaccess) 
  filter(household_tbl, !rightsharvest%in%c(yes_no_codes, skipcodes)) %>%
           select(householdid, rightsharvest) 
  filter(household_tbl, !rightsmanage%in%c(yes_no_codes, skipcodes)) %>%
           select(householdid, rightsmanage) 
  filter(household_tbl, !rightsexclude%in%c(yes_no_codes, skipcodes)) %>%
           select(householdid, rightsexclude) 
  filter(household_tbl, !rightstransfer%in%c(yes_no_codes, skipcodes)) %>%
           select(householdid, rightstransfer) 
  filter(household_tbl, !marinegroup%in%c(yes_no_codes, skipcodes)) %>%
           select(householdid, marinegroup) 
  filter(household_tbl, !othergroup%in%c(yes_no_codes, skipcodes)) %>%
           select(householdid, othergroup) 
  filter(household_tbl, !votedistrict%in%c(yes_no_codes, skipcodes)) %>%
           select(householdid, votedistrict) 
  filter(household_tbl, !votenational%in%c(yes_no_codes, skipcodes)) %>%
           select(householdid, votenational)  

print(paste0("Values out of range for variables with Yes/No choices for Household ID", yes_no_var_index_hh$householdid))
print(yes_no_var_index_hh)
```


```{r}
rights_manage_index <- 
    filter(household_tbl, !rightsmanage%in%c(yes_no_codes, skipcodes)) %>%
           select(householdid, rightsmanage)
print(rights_manage_index)
```

* FS_CHOICES (`fsnotenough`, `fsdidnotlast`, `fsbalanceddiet`, `fslowcostfood`, `fsnomealchild`)

```{r}
fs_codes <- c(1:3)
fs_var_index <- 
  filter(household_tbl, !fsnotenough%in%c(fs_codes, skipcodes)) %>%
           select(householdid, fsnotenough)
  filter(household_tbl, !fsdidnotlast%in%c(fs_codes, skipcodes)) %>%
           select(householdid, fsdidnotlast)
  filter(household_tbl, !fsbalanceddiet%in%c(fs_codes, skipcodes)) %>%
           select(householdid, fsbalanceddiet) 
  filter(household_tbl, !fslowcostfood%in%c(fs_codes, skipcodes)) %>%
           select(householdid, fslowcostfood)
  filter(household_tbl, !fsnomealchild%in%c(fs_codes, skipcodes)) %>%
           select(householdid, fsnomealchild)
  
print(paste0("Values out of range for variables with FS choices for Household ID", fs_var_index$householdid))
print(fs_var_index)
```
    
* FS_FREQ_CHOICES (`fsfreqadultskip`, `fsfreqchildskip`)

```{r}
fs_freq_codes <- c(1:3)
fs_freq_var_index <- 
  filter(household_tbl, !fsfreqadultskip%in%c(fs_freq_codes, skipcodes)) %>%
           select(householdid, fsfreqadultskip)
  filter(household_tbl, !fsfreqchildskip%in%c(fs_freq_codes, skipcodes)) %>%
           select(householdid, fsfreqchildskip)
  
print(paste0("Values out of range for variables with FS_FREQ choices for Household ID", fs_freq_var_index$householdid))
print(fs_freq_var_index)
```

* SOCIAL_CONFLICT_CHOICES (`socialconflict`)

```{r}
social_conflict_codes <- c(1:5)
social_conflict_index <- 
    filter(household_tbl, !socialconflict%in%c(social_conflict_codes, skipcodes)) %>%
           select(householdid, socialconflict)
print(paste0("Values out of range for social conflict for Household ID", social_conflict_index$householdid))
print(social_conflict_index)
```

* ATT_SCALE_CHOICES (`placehappy`, `placefavourite`, `placemiss`, `placebest`, `placefishhere`, `placebemyself`)

```{r}
att_scale_codes <- c(1:5)
att_scale_index <- 
  filter(household_tbl, !placehappy%in%c(att_scale_codes, skipcodes)) %>%
           select(householdid, placehappy)
  filter(household_tbl, !placefavourite%in%c(att_scale_codes, skipcodes)) %>%
           select(householdid, placefavourite)
  filter(household_tbl, !placemiss%in%c(att_scale_codes, skipcodes)) %>%
           select(householdid, placemiss) 
  filter(household_tbl, !placebest%in%c(att_scale_codes, skipcodes)) %>%
           select(householdid, placebest)
  filter(household_tbl, !placefishhere%in%c(att_scale_codes, skipcodes)) %>%
           select(householdid, placefishhere)
  filter(household_tbl, !placebemyself%in%c(att_scale_codes, skipcodes)) %>%
           select(householdid, placebemyself)
  
print(paste0("Values out of range for variables with ATT_SCALE choices for Household ID", att_scale_index$householdid))
print(att_scale_index)
```


# export to a summary table

```{r}
error_dat <- join_all(list(religion_index, latdeg_index, londeg_index, latmin_index, latsec_index, lonmin_index, lonsec_index,  latfrac_index, lonfrac_index, lat_sphere_index, lon_sphere_index,
  day_index, month_index, year_index,
  econ_trend_index, cooking_fuel_index,
  yes_no_var_index_hh,
  rights_manage_index,
  fs_var_index,
  fs_freq_var_index,
  social_conflict_index,
  att_scale_index),
  by='householdid', type='full')
error_dat_reshaped <- melt(error_dat, na.rm = TRUE, id = "householdid")
out_tab <- data.frame(cbind(error_dat_reshaped, error_msg='Value out of range'))

write.xlsx(out_tab, "household_tbl_erroneous_entries.xlsx")
```







