---
output: 
  md_document:
    variant: markdown_github
---

# MPAMystery README


Welcome to WWF's Conservation Evidence Team's MPAMystery repository!  

The [MPA Mystery project](mpamystery.org) is an interdisciplinary research initiative seeking to answer the question of why some MPAs are successful and others fail to provide win-win benefits of conservation and poverty alleviation.  It is a collaboration of social and ecological scientists helping to facilitate and analyze results from well-designed quasi-experimental monitoring in Indonesia and leading global synthesis studies.  

The overall hypothesis of this study is that better governance leads to better outcomes.  With a growing list of publications and other resources, a GitHub repository has proven to be the best place to store the code for 1.) quality control and data management protocols for large, multi-year databases, 2.) basic descriptive analyses, 3.) statistical analyses, and 4.) resulting figures and plots used for reports.  These outputs seek to provide decision-makers with the knowledge they need to design and implement policies that promote the long-term sustainability of marine resources.  

For further detailed information on this repository (and Git/GitHub in general), please visit the associated [Wiki page](https://github.com/WWF-ConsEvidence/MPAMystery/wiki).  



```{r fig.width=5,fig.height=5}

print(c(1,2,3))

```



```{r}

```

