---
title: "R Guide for MPA Mystery Project"
author: "Kelly Claborn"
date: "March 13, 2018"
output: html_document
---

## Workflow / Organization
### GitHub Workflows 

- Centralized
- Feature Branch
- Gitflow
- Forking

Branching at lowest folder level (e.g., social.matching branch)
Pull requests 
  - Tagging specific collaborators -- be very intentional about who is meant to review code
    - earlier in the pipeline of sourced code, might require more eyes

### File Structure

Data wrangling
  - Social
    - QAQC 
    - Sourcing flat data / establish ODBC, etc.
    - Calculating indicators
      - BHS_MPA_Mystery.R
      - SBS_MPA_Mystery.R
  - Ecological
    - Sourcing flat data / establish ODBC, etc.
    - Calculating indicators
  - Cross-cutting
    - Merge soc/eco
  
Functions
  - Plotting functions
    - Global plot themes, guides
  - Aggregating / wrangling
  - Analysis
  
  Every function is its own script (or set of functions that always work together)
  
Analysis
  - Social
    - Experimental analyses
    - Status and trends
    - Matching (end of matching scripts would be output of matching model (pairs) being properly checked and verified -- treatment effects                live in post-matching analysis)
    - Post-matching analysis
  - Ecological
  - Cross-cutting
  
Products
  - Social 
    - status and trends reports
    - impact summaries
  - Ecological
  - Cross-cutting

### File Naming Conventions

Underscores between components of file names

### What to include at the top of every script/Rmd

Code title
Author
Date created
Date modified
Inputs / dependencies
Outputs
  - Any object that isn't removed by end of script (mostly thinking of data frames)
Main sections

### When to create a new script vs. continuing in old one

Think of scripts as one-concept.  One Markdown chunk. 

## Style Guide
### Object naming conventions

For all objects, use periods between components of the name.

- For data frames and other named objects: 
Include types of variables included in object, treatment/methodology, geography (if applicable -- i.e. MPA name), grouping variable (e.g., ".bySett"), time, object type (.df, .mat, etc.)

- For variable names: 
Include standardized reference to variable (e.g., "hfs"), any manipulation that has been done on the variable (e.g., "att"), and any time component as needed (e.g., "t2")

- For functions:

NEVER name something the same thing as somewhere else. 

### Creating sections



Model after the example section below:

```{r}

# 
# ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
#
# ---- SECTION 1: LOAD LIBRARIES & DATA ----
# 
# ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
# 


# ---- 1.1 Import libraries ----

# Insert one line between sub-section title and beginning of code
# NOTE: if you want to provide more separation within a sub-section, you can simply use a comment line such as this

# Insert two lines at end of sub-section code, before next sub-section title


# ---- 1.2 Import data ----

```

Four hyphens on either side of the main section title (and each subsequent sub-section title) will ensure that the section is added to the quick-access bar at the bottom of the script pane.

### Spacing

- Between characters
- Line spacing

### Commenting


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


