---
title: "BHS data summaries"
author: "David Gill"
date: "February 13, 2018"
output: html_document
---
Create custom functions, set stringsasFactors as false
```{r eval=F}
# load packages
pacman::p_load(plyr,ggplot2,reshape2,reldist,grid,gridExtra,varhandle,xlsx,Rmisc,
               RODBC,Matching,optmatch,tidyr,RItools,Hmisc,MBESS,rbounds,Kendall,corrplot,cowplot,dplyr)

# Options
options(scipen=999,stringsAsFactors = FALSE)

# Functions
sum2=function(x){sum(x,na.rm=TRUE)}
mean2=function(x){mean(x,na.rm=TRUE)}
Mode <- function(x) {
 ux <- unique(x)
 ux[which.max(tabulate(match(x, ux)))]
}

# groups and summarizes groups into mean,sd,se,se_upper,se_lower
# my_summarize(data,measurement.var,group1,group2..)
my_summarize <- function (.data,x,...) {
  # needed to use variable names in function
  group_var <- quos(...)
  enquo_x <- enquo(x)  # measurement variable
  mean_name <- paste0(quo_name(enquo_x)) # renaming variables
  # group and summarize
    .data %>%
    group_by(!!!group_var) %>% 
    summarise(m= mean(UQ(enquo_x)), med=median(UQ(enquo_x)),mode=Mode(UQ(enquo_x)),
              sd= sd(UQ(enquo_x)),n=n(), se=sd/sqrt(n),ci=qt(0.975,df=n-1)*se,
              se_lower=m-se,se_upper=m+se,ci_lower=m-ci,ci_upper=m+ci)  %>% 
    rename(!!mean_name:=m)
}


# my_barplot(data,'x','y') # Bar plot with standard error bars
my_barplot_se <- function(.data,x,y){
ggplot(.data,aes_string(x=x,y=y,label='n')) + 
  geom_bar(stat="identity", position =pd, fill='blue')+ theme_bw() +
   geom_line( position = pd) +
   geom_errorbar(aes(ymin=se_upper, ymax=se_lower), width=0.2, position = pd ) +
  geom_text(size = 3, position = position_stack(vjust = 0.5), col='white') 
}

# my_barplot_ci(data,'x','y') # Bar plot with 95% confidence intervals
my_barplot_ci<- function(.data,x,y){
ggplot(.data,aes_string(x=x,y=y,label='n')) + 
  geom_bar(stat="identity", position =pd, fill='blue')+ theme_bw() +
   geom_line( position = pd) +
   geom_errorbar(aes(ymin=ci_upper, ymax=ci_lower), width=0.2, position = pd ) +
  geom_text(size = 3, position = position_stack(vjust = 0.5), col='white') 
}

# my_pointplot_se(.data,'x','y','group.var') # plot with points and standard errors
my_pointplot_se<- function(.data,x,y,group.var){
ggplot(.data,aes_string(x=x,y=y,group=group.var,label='n')) + 
  geom_errorbar(aes(ymin=se_lower, ymax=se_upper), width=0, position = pd ) +
  geom_line(position =pd) +
  geom_point(size=2, position =pd)+ theme_bw() +
  geom_text(size = 3, position = position_stack(vjust = 0.5)) 
}

# my_pointplot_ci(.data,'x','y','group.var') # plot with points and 95% confidence intervals
my_pointplot_ci<- function(.data,x,y,group.var){
ggplot(.data,aes_string(x=x,y=y,group=group.var,label='n')) + 
  geom_errorbar(aes(ymin=ci_lower, ymax=ci_upper), width=0, position = pd ) +
  geom_line(position =pd) +
  geom_point(size=2, position =pd)+ theme_bw() +
  geom_text(size = 3, position = position_stack(vjust = 0.5)) 
}

# Directories
outputdir <- "C:/Users/dgill6/Documents/Data analysis/BHS/"

# ggplot variables
pd <- position_dodge(width=.3) # move them .05 to the left and right
myColors <- matrix(c('deepskyblue3','darkblue'),nrow=1)

```



### Correlations between tenure indicators
```{r eval=F}
tenure <- HHData %>% 
  dplyr::select(MonitoringYear,RightsAccessClean:RightsTransferClean)
names(tenure) <- gsub('Rights','',names(tenure))
names(tenure) <- gsub('Clean','',names(tenure))
is.na(tenure[,2:6])<-tenure[,2:6]>1
tenure <- tenure[complete.cases(tenure),]
summary(tenure)

#for continuous variables
pairs(tenure[,-1])

# Correlograms for the binary tenure variables ()
#jpeg(paste0(outputdir,'tenure_corr_time.jpg'), width = 1024, height = 480, units = "px")
#par(mfrow=c(1,3))
corrplot.mixed(cor(tenure %>% 
             filter(MonitoringYear=="Baseline") %>% 
             dplyr::select(-MonitoringYear),method='spearman',use="pairwise.complete.obs"),
             title="Baseline")
corrplot.mixed(cor(tenure %>% 
             filter(MonitoringYear=="2 Year Post") %>% 
             dplyr::select(-MonitoringYear),method='spearman',use="pairwise.complete.obs"),
             title="two year")
corrplot.mixed(cor(tenure %>% 
             filter(MonitoringYear=="4 Year Post") %>% 
             dplyr::select(-MonitoringYear),method='spearman',use="pairwise.complete.obs"),
             title="four year")
#dev.off()
```


### Trends summaries
```{r eval=F}
# Food security trends
foodsec <- HHData %>% 
 left_join(dplyr::select(BigFive,HouseholdID,MAIndex:SERate),by='HouseholdID')  %>% 
 left_join(MPANames,by='MPAID') %>%
 filter(!is.na(FSIndex)) %>% 
 my_summarize(FSIndex,MonitoringYear,MPAName)

p.foodsec <- my_barplot_se(foodsec,'MonitoringYear','FSIndex') +
  facet_grid(.~MPAName) 
p.foodsec

# Tenure trends
tenure <- HHData %>% 
   left_join(dplyr::select(BigFive,HouseholdID,MAIndex:SERate),by='HouseholdID')  %>% 
   left_join(MPANames,by='MPAID') %>%
   filter(!is.na(MTIndex) & MTIndex<=5) %>% 
  my_summarize(MTIndex,MonitoringYear,MPAName)

p.tenure <- t.plot(tenure,'MonitoringYear','MTIndex') +
  facet_grid(.~MPAName) 
p.tenure

# Income from fishing trends
fincome <- HHData %>% 
   left_join(dplyr::select(BigFive,HouseholdID,MAIndex:SERate),by='HouseholdID')  %>% 
   left_join(MPANames,by='MPAID') %>%
    filter(!is.na(PercentIncFishClean) & PercentIncFishClean!=0) %>% 
  my_summarize(PercentIncFishClean,MonitoringYear,MPAName)

p.fincome <- t.plot(fincome,'MonitoringYear','PercentIncFishClean') +
  ylab("Percent Inc Fishing") +
  xlab("MonitoringYear") +
  facet_grid(.~MPAName) 
p.fincome

fishprot <- HHData %>% 
   left_join(dplyr::select(BigFive,HouseholdID,MAIndex:SERate),by='HouseholdID')  %>% 
   left_join(MPANames,by='MPAID') %>%
   filter(!is.na(PercentProteinFishClean)) %>% 
  my_summarize(PercentProteinFishClean,MonitoringYear,MPAName)

p.fishprot <- t.plot(fishprot,'MonitoringYear','PercentProteinFishClean') +
  ylab("Percent Protein from fish") +
  xlab("MonitoringYear") +
  facet_grid(.~MPAName) 
p.fishprot
  
plot_grid(p.foodsec,p.tenure, labels=c("a", "b"), ncol = 1, nrow = 2)
ggsave(paste0(outputdir,"food_sec_and_tenure.png"),width = 14,height = 7)

plot_grid(p.fincome,p.fishprot, labels=c("a", "b"), ncol = 1, nrow = 2)
ggsave(paste0(outputdir,"fish_income_protein.png"),width = 14,height = 7)
   

plot_grid(p.foodsec, labels=c("a"), ncol = 1, nrow = 2)
ggsave(paste0(outputdir,"food_security.png"),width = 13,height = 7)
 
```

### Food security trend  relationships
##### Food security different based on primary occupation?
```{r eval=F}
prim.occ.data <- HHData %>% 
  left_join(dplyr::select(BigFive,HouseholdID,MAIndex:SERate),by='HouseholdID')  %>% 
  left_join(MPANames,by='MPAID') %>%
  filter(!is.na(PrimaryLivelihoodClean)) %>% 
  mutate(lvlhds=recode(PrimaryLivelihoodClean,'1'='farming','2'='forest_harvesting','3'='fishing',
                       '4'='aquaculture','5'='mining','6'='tourism','7'='wage_labor','996'="other")) %>%   my_summarize(FSIndex,MPAName,lvlhds,MonitoringYear)

p.priocc <- my_pointplot_ci(prim.occ.data,'MonitoringYear','FSIndex','MPAName') +
  ylab("FSIndex") +
  xlab("MonitoringYear") +
  annotate("rect", xmin = 0, xmax = 4, ymin = 0, ymax = 1.5,alpha = .1,fill='red') +
  annotate("rect", xmin = 0, xmax = 4, ymin = 1.5, ymax = 4,alpha = .1,fill='yellow') +
  annotate("rect", xmin = 0, xmax = 4, ymin = 4, ymax = 6,alpha = .1,fill='green') +
  facet_grid(lvlhds ~ MPAName) 
p.priocc

ggsave(paste0(outputdir,"food security by occupation.png"),width = 15,height = 9)
```

###### Food security different based on income from fishing?
```{r eval=F}
prim.inc <- HHData %>% 
 left_join(dplyr::select(BigFive,HouseholdID,MAIndex:SERate),by='HouseholdID')  %>% 
 left_join(MPANames,by='MPAID') %>% 
 filter(!is.na(PercentIncFishClean) & PercentIncFishClean!=0) %>% 
 mutate(fish.inc=recode_factor(PercentIncFishClean,'1'='none','2'='some','3'='almost half',
                       '4'='most','5'='all',.ordered = T)) %>%
 mutate(fish.inc1=ifelse(PercentIncFishClean>3,'majority','minority')) %>% 
 my_summarize(FSIndex,MPAName,fish.inc,MonitoringYear)


p.primincD <- my_pointplot_se(prim.inc,'MonitoringYear','FSIndex','MPAName') +
              ylab("FSIndex") +
              xlab("MonitoringYear") +
              annotate("rect", xmin = 0, xmax = 4, ymin = 0, ymax = 1.5,alpha = .1,fill='red') +
              annotate("rect", xmin = 0, xmax = 4, ymin = 1.5, ymax = 4,alpha = .1,fill='yellow') +
              annotate("rect", xmin = 0, xmax = 4, ymin = 4, ymax = 6,alpha = .1,fill='green') +
              facet_grid(fish.inc ~ MPAName) 
p.primincD
ggsave(paste0(outputdir,"food security by occupation-detailed.png"),width = 15,height = 9)

prim.inc1 <- HHData %>% 
 left_join(dplyr::select(BigFive,HouseholdID,MAIndex:SERate),by='HouseholdID')  %>% 
 left_join(MPANames,by='MPAID') %>% 
 filter(!is.na(PercentIncFishClean) & PercentIncFishClean!=0) %>% 
 mutate(fish.inc1=ifelse(PercentIncFishClean>3,'majority','minority')) %>% 
 my_summarize(FSIndex,MPAName,fish.inc1,MonitoringYear)
colnames(myColors) <- c("majority","minority")
colScale <- scale_colour_manual(name = "Fish inc.",values =rev(myColors), breaks=c("majority","minority"))

p.priminc <-  ggplot(prim.inc1, aes(x=MonitoringYear, y=FSIndex,label=N,color=fish.inc1)) + 
              geom_errorbar(aes(ymin=FSIndex- se, ymax=FSIndex+ se), width=0, position = pd ) +
              geom_point(size=2, position =pd)+ theme_bw() +
              geom_line(position=pd) +
              geom_text(size = 3, nudge_x=0.5) +
              ylab("FSIndex") +
              xlab("MonitoringYear") +
              annotate("rect", xmin = 0, xmax = 4, ymin = 0, ymax = 1.5,alpha = .1,fill='red') +
              annotate("rect", xmin = 0, xmax = 4, ymin = 1.5, ymax = 4,alpha = .1,fill='yellow') +
              annotate("rect", xmin = 0, xmax = 4, ymin = 4, ymax = 6,alpha = .1,fill='green') +
              facet_grid( ~ MPAName) +
              colScale
p.priminc
ggsave(paste0(outputdir,"food security by occupation.png"),width = 15,height = 7)
```

### Those who rely heavily on fish for protein differ in food security?
```{r eval=F}
most.prot <- HHData %>% 
 left_join(dplyr::select(BigFive,HouseholdID,MAIndex:SERate),by='HouseholdID')  %>% 
 left_join(MPANames,by='MPAID') %>% 
 filter(!is.na(PercentProteinFishClean)) %>% 
 mutate(reliance=ifelse(PercentProteinFishClean>3,'half or more','less half')) %>% 
 summarySE(measurevar="FSIndex", groupvars=c('MPAName','reliance',"MonitoringYear"),na.rm = T)
colnames(myColors) <- c('half or more','less half')
colScale <- scale_colour_manual(name = "Fish prot.",values = myColors,breaks=c('half or more','less half'))

p.most.prot <- ggplot(most.prot, aes(x=MonitoringYear, y=FSIndex,colour=reliance)) + 
    #scale_x_discrete(limits = rev(levels(MPAdata2$No_take))) +
    geom_errorbar(aes(ymin=FSIndex- se, ymax=FSIndex+ se), width=0, position = pd ) +
    geom_line( position = pd ) +
    geom_point(size=2, position =pd)+ theme_bw() +
    ylab("FSIndex") +
    xlab("MonitoringYear") +
    facet_grid(. ~ MPAName) +
    colScale
# + geom_text(x=5.5, y=2, label="a)",col="black")

# Food security different based on market distance?
mrkt.dist <- HHData %>% 
  left_join(dplyr::select(BigFive,HouseholdID,MAIndex:SERate),by='HouseholdID')  %>% 
  left_join(MPANames,by='MPAID') %>% 
  filter(!is.na(TimeMarketClean)) %>% 
  mutate(mrktdist=ifelse(TimeMarketClean>=2,'far','near')) %>% 
  summarySE(measurevar="FSIndex", 
                   groupvars=c('MPAName','mrktdist',"MonitoringYear"), na.rm = T)
colnames(myColors) <- c("far","near")
colScale <- scale_colour_manual(name = "Group",values = rev(myColors),breaks=c("far","near"))

p.mrktdist <- ggplot(mrkt.dist, aes(x=MonitoringYear, y=FSIndex,colour=mrktdist)) + 
  #scale_x_discrete(limits = rev(levels(MPAdata2$No_take))) +
  geom_errorbar(aes(ymin=FSIndex- se, ymax=FSIndex+ se), width=0, position = pd ) +
  geom_line( position = pd ) +
  geom_point(size=2, position =pd)+ theme_bw() +
  ylab("FSIndex") +
  xlab("MonitoringYear") +
  facet_grid(. ~ MPAName) +
  colScale

#---------------
plot_grid(p.prim.inc,p.most.prot, labels=c("a", "b"), ncol = 1, nrow = 2)
ggsave(paste0(outputdir,"food security-income and food dependency.png"),width = 15,height = 5)

p.mrktdist
ggsave(paste0(outputdir,"mrktdist_foodsecurity.png"),width = 15,height = 5)
```

#### Food security differ by tenure?
```{r eval=F}
table(HHData$RightsAccessCoded)

t.access <- HHData %>% 
  left_join(dplyr::select(BigFive,HouseholdID,MAIndex:SERate),by='HouseholdID')  %>% 
  left_join(MPANames,by='MPAID') %>% 
  filter(RightsAccessCoded%in%c(0,1)) %>% 
  mutate(access=ifelse(RightsAccessCoded==1,'yes','no'))

# Plot all MPAs
t.access2 <- summarySE(t.access, measurevar="FSIndex", groupvars=c('access',"MonitoringYear"),na.rm = T)
pd <- position_dodge(width=.3) # move them .05 to the left and right
myColors <- matrix(c('deepskyblue3','darkblue'),nrow=1)
colnames(myColors) <- c("yes","no")
colScale <- scale_colour_manual(name = "Access",values = myColors,breaks=c("yes","no"))

p.access <- ggplot(t.access2, aes(x=MonitoringYear, y=FSIndex,colour=access)) + 
  #scale_x_discrete(limits = rev(levels(MPAdata2$No_take))) +
  geom_errorbar(aes(ymin=FSIndex- se, ymax=FSIndex+ se), width=0, position = pd ) +
  geom_line( position = pd ) +
  geom_point(size=2, position =pd)+ theme_bw() +
  ylab("FSIndex") +
  xlab("MonitoringYear") +
  colScale

# Plot by MPA
t.access3 <- summarySE(t.access, measurevar="FSIndex", groupvars=c('MPAName','access',"MonitoringYear"),na.rm = T)

p.access.MPA <- ggplot(t.access3, aes(x=MonitoringYear, y=FSIndex,colour=access)) + 
  #scale_x_discrete(limits = rev(levels(MPAdata2$No_take))) +
  geom_errorbar(aes(ymin=FSIndex- se, ymax=FSIndex+ se), width=0, position = pd ) +
  geom_line( position = pd ) +
  geom_point(size=2, position =pd)+ theme_bw() +
  ylab("FSIndex") +
  xlab("MonitoringYear") +
  facet_grid(. ~ MPAName) +
  colScale

##Harvest rights
t.harvest <- HHData %>% 
  left_join(dplyr::select(BigFive,HouseholdID,MAIndex:SERate),by='HouseholdID')  %>% 
  left_join(MPANames,by='MPAID') %>% 
  filter(RightsHarvestClean%in%c(0,1)) %>% 
  mutate(harvest=ifelse(RightsHarvestClean==1,'yes','no'))

# Plot all MPAs
t.harvest2 <- summarySE(t.harvest, measurevar="FSIndex", groupvars=c('harvest',"MonitoringYear"),na.rm = T)
colScale <- scale_colour_manual(name = "harvest",values = myColors,breaks=c("yes","no"))

p.harvest <- ggplot(t.harvest2, aes(x=MonitoringYear, y=FSIndex,colour=harvest)) + 
  #scale_x_discrete(limits = rev(levels(MPAdata2$No_take))) +
  geom_errorbar(aes(ymin=FSIndex- se, ymax=FSIndex+ se), width=0, position = pd ) +
  geom_line( position = pd ) +
  geom_point(size=2, position =pd)+ theme_bw() +
  ylab("FSIndex") +
  xlab("MonitoringYear") +
  colScale

# Plot by MPA
t.harvest3 <- summarySE(t.harvest, measurevar="FSIndex", groupvars=c('MPAName','harvest',"MonitoringYear"),na.rm = T)

p.harvest.MPA <- ggplot(t.harvest3, aes(x=MonitoringYear, y=FSIndex,colour=harvest)) + 
  #scale_x_discrete(limits = rev(levels(MPAdata2$No_take))) +
  geom_errorbar(aes(ymin=FSIndex- se, ymax=FSIndex+ se), width=0, position = pd ) +
  geom_line( position = pd ) +
  geom_point(size=2, position =pd)+ theme_bw() +
  ylab("FSIndex") +
  xlab("MonitoringYear") +
  facet_grid(. ~ MPAName) +
  colScale
## Managment rights
t.manage <- HHData %>% 
  left_join(dplyr::select(BigFive,HouseholdID,MAIndex:SERate),by='HouseholdID')  %>% 
  left_join(MPANames,by='MPAID') %>% 
  filter(RightsManageClean%in%c(0,1)) %>% 
  mutate(manage=ifelse(RightsManageClean==1,'yes','no'))

# Plot all MPAs
t.manage2 <- summarySE(t.manage, measurevar="FSIndex", groupvars=c('manage',"MonitoringYear"),na.rm = T)
colScale <- scale_colour_manual(name = "manage",values = myColors,breaks=c("yes","no"))

p.manage <- ggplot(t.manage2, aes(x=MonitoringYear, y=FSIndex,colour=manage)) + 
  #scale_x_discrete(limits = rev(levels(MPAdata2$No_take))) +
  geom_errorbar(aes(ymin=FSIndex- se, ymax=FSIndex+ se), width=0, position = pd ) +
  geom_line( position = pd ) +
  geom_point(size=2, position =pd)+ theme_bw() +
  ylab("FSIndex") +
  xlab("MonitoringYear") +
  colScale

# Plot by MPA
t.manage3 <- summarySE(t.manage, measurevar="FSIndex", groupvars=c('MPAName','manage',"MonitoringYear"),na.rm = T)

p.manage.MPA <- ggplot(t.manage3, aes(x=MonitoringYear, y=FSIndex,colour=manage)) + 
  #scale_x_discrete(limits = rev(levels(MPAdata2$No_take))) +
  geom_errorbar(aes(ymin=FSIndex- se, ymax=FSIndex+ se), width=0, position = pd ) +
  geom_line( position = pd ) +
  geom_point(size=2, position =pd)+ theme_bw() +
  ylab("FSIndex") +
  xlab("MonitoringYear") +
  facet_grid(. ~ MPAName) +
  colScale

##Exclude rights
t.exclude <- HHData %>% 
  left_join(dplyr::select(BigFive,HouseholdID,MAIndex:SERate),by='HouseholdID')  %>% 
  left_join(MPANames,by='MPAID') %>% 
  filter(RightsExcludeClean%in%c(0,1)) %>% 
  mutate(exclude=ifelse(RightsExcludeClean==1,'yes','no'))

# Plot all MPAs
t.exclude2 <- summarySE(t.exclude, measurevar="FSIndex", groupvars=c('exclude',"MonitoringYear"),na.rm = T)
colScale <- scale_colour_manual(name = "exclude",values = myColors,breaks=c("yes","no"))

p.exclude <- ggplot(t.exclude2, aes(x=MonitoringYear, y=FSIndex,colour=exclude)) + 
  #scale_x_discrete(limits = rev(levels(MPAdata2$No_take))) +
  geom_errorbar(aes(ymin=FSIndex- se, ymax=FSIndex+ se), width=0, position = pd ) +
  geom_line( position = pd ) +
  geom_point(size=2, position =pd)+ theme_bw() +
  ylab("FSIndex") +
  xlab("MonitoringYear") +
  colScale

# Plot by MPA
t.exclude3 <- summarySE(t.exclude, measurevar="FSIndex", groupvars=c('MPAName','exclude',"MonitoringYear"),na.rm = T)

p.exclude.MPA <- ggplot(t.exclude3, aes(x=MonitoringYear, y=FSIndex,colour=exclude)) + 
  #scale_x_discrete(limits = rev(levels(MPAdata2$No_take))) +
  geom_errorbar(aes(ymin=FSIndex- se, ymax=FSIndex+ se), width=0, position = pd ) +
  geom_line( position = pd ) +
  geom_point(size=2, position =pd)+ theme_bw() +
  ylab("FSIndex") +
  xlab("MonitoringYear") +
  facet_grid(. ~ MPAName) +
  colScale

##Transfer rights
t.transfer <- HHData %>% 
  left_join(dplyr::select(BigFive,HouseholdID,MAIndex:SERate),by='HouseholdID')  %>% 
  left_join(MPANames,by='MPAID') %>% 
  filter(RightsTransferClean%in%c(0,1)) %>% 
  mutate(transfer=ifelse(RightsTransferClean==1,'yes','no'))

# Plot all MPAs
t.transfer2 <- summarySE(t.transfer, measurevar="FSIndex", groupvars=c('transfer',"MonitoringYear"),na.rm = T)
colScale <- scale_colour_manual(name = "transfer",values = myColors,breaks=c("yes","no"))

p.transfer <- ggplot(t.transfer2, aes(x=MonitoringYear, y=FSIndex,colour=transfer)) + 
  #scale_x_discrete(limits = rev(levels(MPAdata2$No_take))) +
  geom_errorbar(aes(ymin=FSIndex- se, ymax=FSIndex+ se), width=0, position = pd ) +
  geom_line( position = pd ) +
  geom_point(size=2, position =pd)+ theme_bw() +
  ylab("FSIndex") +
  xlab("MonitoringYear") +
  colScale

# Plot by MPA
t.transfer3 <- summarySE(t.transfer, measurevar="FSIndex", groupvars=c('MPAName','transfer',"MonitoringYear"),na.rm = T)

p.transfer.MPA <- ggplot(t.transfer3, aes(x=MonitoringYear, y=FSIndex,colour=transfer)) + 
  #scale_x_discrete(limits = rev(levels(MPAdata2$No_take))) +
  geom_errorbar(aes(ymin=FSIndex- se, ymax=FSIndex+ se), width=0, position = pd ) +
  geom_line( position = pd ) +
  geom_point(size=2, position =pd)+ theme_bw() +
  ylab("FSIndex") +
  xlab("MonitoringYear") +
  facet_grid(. ~ MPAName) +
  colScale


plot_grid(p.access,p.harvest,p.manage,p.exclude,p.transfer+ theme(legend.position="right"),
           labels=letters[1:5], ncol = 2, nrow = 3)
ggsave(paste0(outputdir,"tenure_foodsecurity.png"),width = 10,height = 7)
```



### other functions
```{r eval=F}
# Correlogram
plot.cor <- function (x){
  M <- cor(x,method='spearman',use="pairwise.complete.obs")
  #arrange by hierarchical clusters
  ord <-   corrMatOrder(M, order="hclust")
  M1 <- M[ord, ord]
  #get correlation p-values, in same order
  pval <- psych::corr.test(x, adjust="none",use = "pairwise",method="spearman")$p[ord, ord]
  #psych::corr.test(Mgt_latest2[,c('STF','BGT')], adjust="none",use = "pairwise",method="spearman")$p
  
  # corrplot(M1, tl.pos="lt",method = "number",type='lower',order = "original",title = "",
  #          p.mat = pval , insig = "blank")
  # corrplot(M1, tl.pos="n",diag=F,add=T,method = "circle",type='upper',order = "original",title = "",
  #          p.mat = pval , insig = "blank",cl.pos="n")
   corrplot.mixed(M,order='hclust')
  }


```