---
title: "Quality checking Source data"
author: "David Gill"
date: "6/12/2019"
output: html_document
---

```{r setup, include=FALSE}
getwd()
knitr::opts_knit$set(root.dir = getwd())
```

Script that goes through the relevant variables in the Wellbeing and Demographic tables to ensure that all variables are recoded correctly in the Source_social_data_flat_files.R script. 

### ---- SECTION 1 Load libraries and import data 
```{r warning=FALSE, echo=FALSE}
pacman::p_load(dplyr,rio)

# Files (with package rio)
last.file <- function(dir.nam,nam){
  import(paste0(dir.nam,last(sort(grep(nam,list.files(dir.nam), value=T)))))}


WELLBEING <- last.file(dir.nam='x_Flat_data_files/1_Social/Inputs/Master_database_exports/',nam='HH_tbl_WELLBEING')
DEMOGRAPHIC <- last.file(dir.nam='x_Flat_data_files/1_Social/Inputs/Master_database_exports/',nam='HH_tbl_DEMOGRAPHIC')
SETTLEMENT <- last.file(dir.nam='x_Flat_data_files/1_Social/Inputs/Master_database_exports/',nam='HH_tbl_SETTLEMENT')
ORGANIZATION <- last.file(dir.nam='x_Flat_data_files/1_Social/Inputs/Master_database_exports/',nam='HH_tbl_ORGANIZATION')
```


### ---- SECTION 2: GET SUMMARIES AND UNIQUE VALUES FROM TABLES 
Prints out summaries, unique values, and headers for the wellbeing and demographic tables 

#### 2.1 Wellbeing table
```{r echo=FALSE}

for (i in 1:ncol(WELLBEING)){
  
  print(paste0(names(WELLBEING)[i]," (",class(WELLBEING[,i]),")"))
  
  if(length(unique(WELLBEING[,i]))>25 & class(WELLBEING[,i])!="character"){
    print(summary(WELLBEING[,i]))
  }
  
  else{
    if (length(unique(WELLBEING[,i]))<25){
      print(table(WELLBEING[,i]))}
    else{
      print(head(WELLBEING[,i]))}
  }
}

```
#### 2.2 Demographic table
```{r echo=FALSE}

for (i in 1:ncol(DEMOGRAPHIC)){
  
  print(paste0(names(DEMOGRAPHIC)[i]," (",class(DEMOGRAPHIC[,i]),")"))
  
  if(length(unique(DEMOGRAPHIC[,i]))>25 & class(DEMOGRAPHIC[,i])!="character"){
    print(summary(DEMOGRAPHIC[,i]))
  }
  
  else{
    if (length(unique(DEMOGRAPHIC[,i]))<25){
      print(table(DEMOGRAPHIC[,i]))}
    else{
      print(head(DEMOGRAPHIC[,i]))}
  }
}

```

#### 3. Display incorrect values
```{r echo=FALSE}
blind.codes <- c(994,997,998,999)


```
